Cluster Analysis: Identifying Parkinson's Disease Subtypes

### 2015-06-24 writeup/parkinsons.tex
update pdf to include new data

\documentclass[letterpaper,12pt]{article}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
% Random packages from
% http://tex.stackexchange.com/questions/50070/landscape-figure-in-latex
% Necessary for sideways pictures
\usepackage{wrapfig}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{epstopdf}
\usepackage{tablefootnote}
% for word wrap verbatim
\usepackage{listings}
\lstset{
   breaklines=true,
   basicstyle=\ttfamily}
% \pagestyle{fancy}
% \lhead{Jesse Mu}
% \rhead{CSCI339 Term Project}
\graphicspath{ {../figures/} }

@@

\section{Biclustering}

>>>>

\documentclass[letterpaper,12pt]{article}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{numprint}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
% Random packages from
% http://tex.stackexchange.com/questions/50070/landscape-figure-in-latex
% Necessary for sideways pictures
\usepackage{wrapfig}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{epstopdf}
\usepackage{tablefootnote}
% for word wrap verbatim
\usepackage{listings}
\lstset{
   breaklines=true,
   basicstyle=\ttfamily}
% \pagestyle{fancy}
% \lhead{Jesse Mu}
% \rhead{CSCI339 Term Project}
\graphicspath{ {../figures/} }
% Or this, if run from main folder
% \graphicspath{ {./figures/} }

@@

\subsection{Summary Statistics based on Clusters}

\begin{lstlisting}
k = 2, cluster 1
var,mean,sd,min,max
age,68.38,9.4,42,89
sex,0.43,0.5,0,1
pdonset,57.65,10.81,32,87
durat_pd,10.73,7.14,0,40
cisitot,13.07,4.55,2,24
k = 2, cluster 2
var,mean,sd,min,max
age,63.43,9.55,37,89
sex,0.36,0.48,0,1
pdonset,56.44,10.62,28,89
durat_pd,6.99,4.94,0,28
cisitot,6.64,3.42,0,16

k = 3, cluster 1
var,mean,sd,min,max
age,62.69,9.43,37,89
sex,0.39,0.49,0,1
pdonset,56.04,10.41,28,89
durat_pd,6.65,4.66,0,26
cisitot,5.76,3.15,0,15
k = 3, cluster 2
var,mean,sd,min,max
age,66.17,9.74,38,86
sex,0.32,0.47,0,1
pdonset,57.78,11.19,32,84
durat_pd,8.39,5.79,0,31
cisitot,9.95,3.5,2,22
k = 3, cluster 3
var,mean,sd,min,max
age,68.62,9.2,50,89
sex,0.46,0.5,0,1
pdonset,57.24,10.46,35,87
durat_pd,11.38,7.52,0,40
cisitot,13.52,5.01,2,24

k = 4, cluster 1
var,mean,sd,min,max
age,71.9,8.1,54,89
sex,0.46,0.5,0,1
pdonset,58.28,10.27,35,87
durat_pd,13.62,7.76,0,40
cisitot,16.72,4.14,4,24
k = 4, cluster 2
var,mean,sd,min,max
age,62.65,9.63,37,89
sex,0.36,0.48,0,1
pdonset,56.13,10.47,28,89
durat_pd,6.52,4.66,0,25
cisitot,5.58,3.12,0,15
k = 4, cluster 3
var,mean,sd,min,max
age,64.79,9.3,44,86
sex,0.47,0.5,0,1
pdonset,56.2,10.71,35,85
durat_pd,8.59,6.16,0,27
cisitot,9.23,3.88,2,19
k = 4, cluster 4
var,mean,sd,min,max
age,66.27,9.47,40,86
sex,0.33,0.47,0,1
pdonset,57.84,11.06,32,84
durat_pd,8.43,5.64,0,31
cisitot,10.06,3.49,3,22
\end{lstlisting}
\section{Biclustering}

Used BCBimax clustering algorithm. Clusters seem quite sparse.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{biclust-16.pdf}
  \caption{Biclustering $N = 16$}
  \label{fig:biclust-16}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{bubbleplot-16.pdf}
  \caption{Bubbleplot $N = 16$}
  \label{fig:bubbleplot-16}
\end{figure}
